Assessing exposure to Atlantic Basin tropical storms in United States counties

### 2016-07-18 writing/DraftExposurePaper/DraftExposurePaper.Rmd
wind tables

n <- 4
wind_plots <- lapply(wind_exposed$storm_id[1:n], top_wind_exposed)
names(wind_plots) <- letters[1:n]
grid.arrange(wind_plots$a, wind_plots$b, wind_plots$c,
             wind_plots$d, ncol = 2)
```
#### Is our 3-day window for rian exposure reasonable?

>>>>

n <- 4
wind_plots <- lapply(wind_exposed$storm_id[1:n], top_wind_exposed)
names(wind_plots) <- letters[1:n]
grid.arrange(wind_plots$a, wind_plots$b, wind_plots$c,
             wind_plots$d, ncol = 2)
```

Here is a table of the top 10 storms by number of counties exposed, based on a wind metric of 33 m/s or greater (e.g., Hurricane strength, category 1 or greater):

all_wind <- county_wind(counties = all_counties, start_year = 1988, 
                        end_year = 2011, wind_limit = 33)

hu_exposed <- all_wind %>%
        group_by(storm_id) %>%
        summarize(number_of_counties_exposed = n()) %>%
        arrange(desc(number_of_counties_exposed)) %>%
        top_n(10)

hu_exposed %>%
        mutate(storm_id = gsub("-", " (", storm_id),
               storm_id = paste0(storm_id, ")")) %>%
        kable(col.names = c("Storm", "# of exposed counties"),
              caption = "Top 10 storms based on the number of counties exposed, using a metric of wind.")
```

Here is a table of the top 10 storms by number of counties exposed, based on a wind metric of 50 m/s or greater (e.g., Intense Hurricane strength, category 3 or greater):

all_wind <- county_wind(counties = all_counties, start_year = 1988, 
                        end_year = 2011, wind_limit = 50)

cat3_exposed <- all_wind %>%
        group_by(storm_id) %>%
        summarize(number_of_counties_exposed = n()) %>%
        arrange(desc(number_of_counties_exposed)) %>%
        top_n(10)

cat3_exposed %>%
        mutate(storm_id = gsub("-", " (", storm_id),
               storm_id = paste0(storm_id, ")")) %>%
        kable(col.names = c("Storm", "# of exposed counties"),
              caption = "Top 10 storms based on the number of counties exposed, using a metric of wind.")
```

For all of the above exposure categories, Lili (1996), Karl (2004), and Ophelia (2005) remained the top 3 storms by number of counties exposed based on the various wind exposure metrics, each with 2396 counties exposed [JMF-- I think something weird is going on here].

#### Is our 3-day window for rian exposure reasonable?
